---
title: "Machine Learning with the Titanic Data Set"
author: "Alex McIntosh"
date: "8/19/2022"
output:
  bookdown::pdf_document2
figsintext : yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # Default to false considering I hope to use mostly graphs
  message = FALSE,
  warning = FALSE,
  tidy = TRUE,
  cahe = TRUE, # Set to FALSE to conserve memory
  eval = TRUE # Set to TRUE for code to actually rune
)
options(digits = 3)
source("src/analysis.R")
```

# Cover Page
<!--
- Title
- Authors and their affiliations
- Contacts
- Name of publisher (if any)
- Date of publication 
--> 
# Table of Contents
# Executive Summary / Abstract
<!-- 
> Nothing is more powerful than explaining the crux of your arguments in three paragraphs or less.
- Set up the problem for the reader
- Follow up of relevant research
- Point out the gap in knowledge being filled 
- Formally introduce research questions and hypothesis
--> 

# Methodology
<!-- 
- Research methods
- Data sources
- Explain new data collection (if any)
- Literature review to defend choice of variables, data, methods 
--> 
```{r numeric_summary}
numeric_summary
```

```{r}
age_histogram
age_surival_rate
sib_sb_histogram
sib_sb_survival_rate
par_ch_histogram
par_ch_survival_rate
fare_histogram
class_bar
sex_bar
embarked_bar
```

<!-- Worth finding a way to add original names back in?-->
```{r}
last_names %>%
  head()
```

```{r}
title_histogram
title_survival_rate
last_name_histogram
last_name_survival_rate
```

```{r}
cabins
```

```{r}
cabin_histogram
cabin_survial_rate
cabin_histogram_facet
```

```{r}
missing_data
```

```{r}
logistic_variable_importance
```

```{r}
rf_variable_importance
```

```{r}
train_ensemble_scatter_plot
```

# Results
<!--
- Descriptive statistics
- Illustrative graphics
- Formally test the hypothesis 
--> 
```{r}
results_scatter_plot
```

```{r}
results
```


```{r}
validation %>%
  head()
```

Score of 0.75837, which in this case was determined by accuracy.
This means that I correctly predicted survival for 317 of the 418 passengers in 
the test set.
0.75837 is significantly lower than the some of the accuracies reached during
model development.
This is a clear indication that the methods were over-trained on the training data
set.

# Discussion
<!--
- Use the results to show how the knowledge gaps introduced in the executive summary have been filled
- Recognize when the results were not as substantial as originally believed
--> 

# Conclusion


<!-- 
- Promote your findings
- Identify possible future research
--> 

# Acknowledgements
<!-- 
- Acknowledging support is never a bad idea 
--> 

# References
# Appendices (if needed)

<!-- 
Publication Checklist:
- [ ] Have you told readers, at the outset, what they might gain by reading your paper?
- [ ] Have you made the aim of your work clear?
- [ ] Have you explained the significance of your contribution?
- [ ] Have you set your work in the appropriate context by giving sufficient background (including a complete set of relevant references) to your work?
- [ ] Have you addressed the question of practicality and usefulness?
- [ ] Have you identified future developments that might result from your work?
- [ ] Have you structured your paper in a clear and logical fashion?
--> 

